---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# kthcorpus

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of `kthcorpus` is to provide some tools that can be used when working with DiVA data. 

## Installation

``` r
remotes::install_git("https://github.com/KTH-Library/kthcorpus", dependencies = TRUE)
```

## Example

This is a basic example which shows you how to use some of these tools:

```{r example, eval=FALSE}
library(kthcorpus)

# download and cache KTH DiVA data
pubs <- kth_diva_pubs()
authors <- kth_diva_authors()
aliases <- kth_diva_aliases()
issues <- kth_diva_issues()

# run some checks
checks <- kth_diva_checks()

# see results
checks
```

# Development

Press "Ctrl-Shift-L" to load function, which can then be run, for example:

```{r, eval = FALSE}
check_invalid_DOI()
# A tibble: 1 x 2
#  DOI                         PID
#  <chr>                     <dbl>
#1 0.1109/ICC.2019.8761470 1498747
```

The cache with downloaded data for publications and author data can be cleared:

```{r, eval = FALSE}
unlink(
  file.path(rappdirs::app_dir("kthcorpus")$config(), 
    c("kth_diva_pubs.rds", "kth_diva_authors.rds")
  )
)
```

## Adding checks

See the file at "`R/checks.R`" for some of the checks. Edit and add checks there.

Checks using Python can be used too, through `reticulate`, for example.

## Running the API locally

To run the API locally, just open the file (located in `inst/plumber/checks/plumber.R`) and press play.

