---
title: "Checks for KTH Corpus"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)

myDT <- function(data) {
  if (is.null(data) || nrow(data) <= 0) 
    return(htmltools::pre("No results found for this check"))
  
  DT::datatable(data, #filter = "top",
    escape = FALSE,
    rownames = FALSE,
    options = list(
      dom = 'pt',
      scrollX = "90vh", scrollY = "80vh")
    )
}

shorten <- function(x, n = 20) {
  if (nchar(x) > n) return(substr(x, 1, n))
  x
}

compact_cols <- function(data) {
  mask_keep <- colSums(!is.na(data)) > 0
  data[, mask_keep, drop = FALSE]
}

```

Checks {.tabset}
-----------------------------------------------------------------------

### Title Multiplettes

```{r}
library(kthcorpus)
library(dplyr)

checks <- kth_diva_checks()

myDT(checks$article_title_multiplettes)
```

### Submission status

```{r}
myDT(checks$submission_status_invalid %>% select(-c(Name, Abstract)) %>% compact_cols())
```

### Missing kthid

```{r}
myDT(checks$missing_kthid)
```

### Missing conference publication dates

```{r}
myDT(checks$missing_confpubdate)
```

### Missing journal ids

```{r}
myDT(checks$missing_journal_ids  %>% select(-c(Name, Abstract)) %>% compact_cols())
```
### Multiplettes for DOI

```{r}
myDT(checks$multiplettes_DOI)
```

### Multiplettes for ScopusID

```{r}
myDT(checks$multiplettes_scopusid)
```

### Multiplettes for ISI

```{r}
myDT(checks$multiplettes_ISI)
```


### Invalid ISI

```{r}
myDT(checks$invalid_ISI)
```

### Invalid DOI

```{r}
myDT(checks$invalid_DOI)
```

### Invalid ISSN

```{r}
myDT(checks$invalid_ISSN)
```

### Invalid org unit id

```{r}
myDT(checks$invalid_orgid)
```

### Uncertain publication status

```{r}
myDT(checks$uncertain_published)
```

### SwePub checks

```{r}
myDT(swepub_checks())
```


### About

This report was generated on `r Sys.time()` and contains results from running checks on KTH Publications downloaded from DiVA.

The data sources used for the check have the following timestamps:

```{r}

knitr::kable(diva_meta())

```

