---
title: "ORCiDs with ambiguous use in DiVA"
author:
  - name: Markus Skyttner
    orcid: 0000-0002-4649-3651
    email: markussk@kth.se
    affiliations:
      - name: KTH Royal Institute of Technology 
        address: Osquars backe 31
        city: Stockholm
        postal-code: 114 28
highlight-style: pygments
format:
  html:
    toc: true
    toc-location: left
    code-fold: true
    html-math-method: katex
    embed-resources: true
    anchor-sections: true
    smooth-scroll: true
    link-external-icon: true
    link-external-newwindow: true
    page-layout: article
  pdf:
    geometry: 
      - top=30mm
      - left=30mm
  docx: default
editor_options: 
  chunk_output_type: console
---

```{r warning=FALSE, results='hide', echo=TRUE}
#| label: load-pkgs
#| code-summary: "Packages"
#| message: false

pkgs <- "
kthcorpus DT bslib leaflet plotly htmltools dplyr
" 

import <- function(x)
 x |> trimws() |> strsplit("\\s+") |> unlist() |>
  lapply(function(x) library(x, character.only = TRUE)) |> 
  invisible()

pkgs |> import()
  
```

```{r}
#| classes: col_wrap
#| echo: FALSE
#| message: FALSE

bs4_card <- function(body, title) {
  div(class = "table-responsive",
    class = "card",
    div(class = "card-header bg-primary", title),
    div(class = "card-body d-flex justify-content-center", body)
  )
}

# plotly_widget <- plot_ly(x = diamonds$cut) %>%
#   config(displayModeBar = FALSE) %>%
#   layout(margin = list(t = 0, b = 0, l = 0, r = 0))
# 
# leaflet_widget <- leaflet() %>%
#   addTiles()
# 
# layout_column_wrap(
#   width = 1/2,
#   navs_tab_card(
#     height = 300, full_screen = TRUE,
#     title = "HTML Widgets",
#     nav(
#       "Plotly", 
#       card_title("A plotly plot", class = "pt-1"),
#       card_body_fill(plotly_widget)
#     ),
#     nav(
#       "Leaflet",
#       card_title("A leaflet plot", class = "pt-1"),
#       card_body_fill(leaflet_widget)
#     ),
#     nav(
#       shiny::icon("circle-info"),
#       "Learn more about",
#       tags$a("htmlwidgets", href = "http://www.htmlwidgets.org/")
#     )
#   ),
#   navs_tab_card(
#     height = 300, full_screen = TRUE,
#     title = "HTML Widgets",
#     nav(
#       "Plotly", 
#       card_title("A plotly plot", class = "pt-1"),
#       card_body_fill(plotly_widget)
#     ),
#     nav(
#       "Leaflet",
#       card_title("A leaflet plot", class = "pt-1"),
#       card_body_fill(leaflet_widget)
#     ),
#     nav(
#       shiny::icon("circle-info"),
#       "Learn more about",
#       tags$a("htmlwidgets", href = "http://www.htmlwidgets.org/")
#     )
#   )
#)
```


```{r}
#| echo: FALSE
#| message: FALSE
#| 
options(DT.options = list(scrollY = "100vh"))

myDT <- function(data) {
  
  if (is.null(data) || nrow(data) <= 0) 
    return(htmltools::pre("Denna kontroll passerar utan anmärkning! 🥳"))

  # remap column display names here, replace iff in map
  displaynamez <- kthcorpus:::check_remap_colnames(colnames(data))
  
  header_cb <- c(
    "function(thead, data, start, end, display){",
    sprintf("  var tooltips = [%s];", toString(paste0("'", names(displaynamez), "'"))),
    "  for(var i = 0; i <= tooltips.length - 1; i++){",
    "    $('th:eq('+i+')',thead).attr('title', tooltips[i]);",
    "  }",
    "}"
  )  
  
  
  colnamez <- stringr::str_trunc(colnames(data), 15)
  font_size <- "80%"
  
  dt <- DT::datatable(data, 
    filter = "top",
    escape = FALSE,
    rownames = FALSE,
    style = "bootstrap",
    # see https://getbootstrap.com/docs/5.1/content/tables/
    class = "table-borderless table-striped table-sm",
    fillContainer = TRUE,
    width = "100%",
    extensions = c(
      "Buttons",  
      "Select",
      "Scroller"
    ),
    colnames = colnamez,
    options = list(
      headerCallback = DT::JS(header_cb),
      dom = "fBlrtip",  # specify content (search box, etc)
#      dom = 'pt',
# l - Length changing
# f - Filtering input
# t - The Table!
# i - Information
# p - Pagination
# r - pRocessing
      scrollX = TRUE, 
      scrollY = "100vh",
      #paging = FALSE,
      #bPaginate = FALSE,
      #deferRender = FALSE,
      scroller = TRUE,
      select = TRUE,
      buttons = list(
        I("colvis"),  
        "csv",  
        "excel",
        list(
          extend = "copy",
          text = 'Copy to clipboard',
          exportOptions = list(modifier = list(selected = TRUE))
        )
      )#,
      #initComplete = htmlwidgets::JS(
      #  "function(settings, json) {",
      #  paste0("$(this.api().table().container()).css({'font-size': '", font_size, "'});"),
      #  "}"
      #)
    )
  )  
  #NB this causes DT to not fill vertically
  #htmltools::div(dt, style = "font-size:80%")  
  dt
}

myTOC <- function(data) {
  
  if (is.null(data) || nrow(data) <= 0) 
    return(htmltools::pre("No TOC to display"))
  
  font_size <- "80%"
  
  DT::datatable(data,
    escape = FALSE,
    rownames = FALSE,
    style = "bootstrap",
    class = "table-borderless table-sm", 
    width = "100%",
    options = list(
      dom = 't',
      searching = FALSE,
      ordering = FALSE,
      #scrollX = TRUE, 
      scrollY = "80vh"
    )
  )  
}


compact_cols <- function(data) {
  mask_keep <- colSums(!is.na(data)) > 0
  data[, mask_keep, drop = FALSE]
}

checks <- kth_diva_checks()

stats <- function(x) 
  checks$stats %>% 
  dplyr::filter(name == x) %>% 
  dplyr::pull(value) %>% 
  (function(x) ifelse(x == 0, "✅",sprintf("(%s)❗", x)))

```

```{css, echo=FALSE}
div.col_wrap div.bslib-column-wrap {
  display: grid;
}
.tooltip-inner {max-width: 500px;}
.dataTables_scrollBody {
    max-height: 100vh !important;
```

```{r}
#| message: false
#| eval: true
#| echo: false

re_orcid <- "^([0-9]{4})+(-)+([0-9]{4})+(-)+([0-9]{4})+(-)+([0-9]{3}[0-9Xx]{1})$"
re_kthid <- "^u1[a-z0-9]{6}$"

authors <- kthcorpus::kth_diva_authors()

# authors with orcid and kthid but some publications do not have kthids assigned

pubs_missing_kthid <- 
  authors |> filter(!is.na(orcid)) |> select(orcid, kthid, name, autid) |> 
    group_by(orcid, name, autid) |> 
    mutate(n_kthid = n_distinct(kthid)) |> 
    arrange(desc(n_kthid)) |> 
    distinct() |> 
    ungroup() |> 
    filter(n_kthid > 1, !grepl("^PI", kthid)) |> 
    left_join(
      authors |> 
        group_by(orcid, kthid, name, autid) |> 
        summarise(pids = paste0(collapse=" ", unique(PID)), n_pids = n_distinct(PID)), 
          by = c("orcid", "kthid", "name", "autid")) |> 
        arrange(desc(orcid), n_kthid, kthid
    )

authors_with_orcid_and_several_kthids <- 
  authors |> filter(!is.na(orcid)) |> 
    group_by(orcid) |> 
    mutate(
      n_kthid = n_distinct(kthid, na.rm = TRUE), 
      kthids = paste0(collapse = " ", na.omit(unique(kthid)))) |> 
    ungroup() |> 
  filter(n_kthid > 1) |> 
  distinct(orcid, kthids)

  # some authors have ORCiD and kthid, but no value for DiVA author id ("authority-person:105170" etc)
authors_missing_diva_authority_person <- 
    authors |> distinct(orcid, kthid, autid, name, PID) |> 
      group_by(orcid, kthid) |> 
       mutate(
        n_aliases = n_distinct(name, na.rm = TRUE),
        n_autid = n_distinct(autid, na.rm = TRUE), 
        n_pids = n_distinct(PID, na.rm = TRUE)) |> 
      filter(n_aliases >= 1, n_autid >= 0, !grepl("^PI", kthid), !is.na(orcid)) |>
      ungroup() |>
      group_by(orcid) |> 
      summarise(
        pids = paste0(collapse = " ", PID),
        autids = paste0(collapse = " ", unique(na.omit(autid))),
        kthids = paste0(collapse = " ", unique(na.omit(kthid))),
        n_kthids = n_distinct(kthid, na.rm = TRUE),
        n_autids = n_distinct(autid, na.rm = TRUE),
        n_pids = n_distinct(PID, na.rm = TRUE)
      ) |> 
      filter(n_autids == 0, n_kthids >= 1) |> 
      arrange(desc(n_pids)) |> 
      mutate(
        combo = paste0(linkify(orcid, target = "ORCID"), " (", kthids, ")")
      ) |>
      select(orcid, combo, kthids, autids, n_pids, n_kthids, pids) 

  # left_join(
  #   authors |> filter(!is.na(orcid)) |> select(orcid, kthid, autid, name, PID) |>
  #     distinct() |>
  #     group_by(orcid, kthid) |>
  #     mutate(
  #       n_aliases = n_distinct(name, na.rm = TRUE),
  #       n_autid = n_distinct(autid, na.rm = TRUE)) |>
  #     filter(n_aliases >= 1, n_autid >= 0, !grepl("^PI", kthid)) |>
  #     ungroup() |>
  #     group_by(orcid) |>
  #     summarise(
  #       pids = paste0(collapse = " ", PID),
  #       autids = paste0(collapse = " ", unique(na.omit(autid))),
  #       kthids = paste0(collapse = " ", unique(na.omit(kthid))),
  #       n_pids = n_distinct(PID, na.rm = TRUE),
  #       n_kthids = n_distinct(kthid, na.rm = TRUE)
  #     ) |>
  #     filter(n_kthids > 1) |>
  #     arrange(desc(n_kthids)) |>
  #     mutate(
  #       combo = paste0(linkify(orcid, target = "ORCID"), " (", kthids, ")")
  #     ) |>
  #     arrange(combo) |>
  #     select(combo, autids, n_pids, n_kthids, pids) 
  # ) 

my_dt3 <- pubs_missing_kthid |> DT::datatable(escape = F)
my_dt4 <- authors_with_orcid_and_several_kthids |> DT::datatable(escape = F)
my_dt5 <- authors_missing_diva_authority_person |> DT::datatable(escape = F)

  # many |>
  #   select(orcid, n_kthid) |> left_join(multiple = "all",
  #   authors |>
  #     group_by(orcid, kthid, name, autid) |>
  #     summarise(
  #       pids = paste0(collapse=" ", unique(PID)),
  #       n_pids = n_distinct(PID)
  #     ),
  #   by = c("orcid")) |> #, "kthid", "name", "autid")) |>
  #   arrange(desc(orcid), n_kthid, kthid)  |>
  #   group_by(orcid) |>
  #   mutate(combo = paste0(collapse = " ", unique(na.omit(kthid)))) |>
  #   ungroup() |>
  #   select(orcid, combo, kthid, everything()) |>
  #   arrange(orcid, combo, desc(n_pids)) |>
  #   mutate(pids = shorten(pids)) |>
  #   #mutate(pids = paste(collapse = " ", linkify(na.omit(pids), target = "PID"))) |>
  #   mutate(orcid = paste0(linkify(orcid, target = "ORCID"), " ", combo)) |>
  #   select(-c("combo", "n_kthid"))

  # many <-
  #   authors |>
  #   group_by(orcid) |>
  #   filter(grepl(re_orcid, orcid)) |>
  #   filter(grepl(re_kthid, kthid)) |>
  #   summarize(
  #     n_kthid = n_distinct(kthid),
  #     kthids =  paste(collapse = " ", unique(kthid)),
  #     n_pids = n_distinct(PID),
  #     pids = paste(collapse = " ", unique(PID))
  #   ) |>
  #   filter(n_kthid > 1) |>
  #   arrange(desc(n_kthid))
  #
  # authors |> inner_join(many, by = "orcid") |> distinct(PID, orcid, kthid) |>
  #   group_by(orcid, kthid) |>
  #   summarise(
  #     pids = paste(collapse = " ", linkify(na.omit(unique(PID)[1:10]), target = "PID")),
  #     n_pids = n_distinct(PID),
  #     kthid = paste(collapse = " ", unique(kthid))
  #   ) |>
  #   group_by(orcid) |>
  #   arrange(orcid, desc(n_pids), orcid) |>
  #   mutate(orcid = linkify(orcid, target = "ORCID")) |>
  #   mutate(combo = paste0(orcid, " (n=", sprintf("%03d", n_pids), ", kthid=", kthid, ")")) |>
  #   ungroup() |>
  #   select(combo, pids)

```


::: {.panel-tabset}

## Multiple kthids

Certain ORCiDs are associated with more than one author at KTH, sometimes because those records are being investigated / checked. Sometimes a possible kthid may be likely, but the investigation is not yet concluded.

:::{.callout-note}
Note that a KTH author may be associated with zero, one (preferably) or in some cases more than one ORCiDs. However, if more than one KTH author identifier make use of the same ORCiD identifier there are chances that an incorrect affiliation has been detected.
:::

```{r}
#| label: tbl-multiple-kthids
#| tbl-cap: "ORCiDs being investigated"
#| message: false
#| column: screen-inset-shaded

my_dt4 <- 
  authors_with_orcid_and_several_kthids |> datatable(
    style = "bootstrap4", # "bootstrap" or "bootstrap4" or "auto" (for bslib)
    class = "table-bordered table-condensed table-sm",
    rownames = FALSE,
    height = "100%",
    escape = FALSE,
    extensions = "RowGroup",
    options = list(
#      rowGroup = list(dataSrc = 0),  # if rownames are used, increase index!
      paging = FALSE,
      dom = "iftr"  # display number of records at top
    ),
    selection = "none"
  )

# Available "dom" settings:
# l - length changing input control
# f - filtering input
# t - The table!
# i - Table information summary
# p - pagination control
# r - processing display element

bs4_card(my_dt4, "Multiple kthids")

```

## Missing DiVA authority person

Authors in DiVA are mostly associated with a "DiVA" authority person identifier. This is not always the case, though. 

:::{.callout-note}
Note that an author with a known kthid will likely have a DiVA authority person identifier. However, sometimes such a record is missing in DiVA.
:::

```{r}
#| label: tbl-missing-authority-person
#| tbl-cap: "Authors with kthid but missing DiVA authority person identifier"
#| message: false
#| column: screen-inset-shaded

my_dt5 <- 
  authors_missing_diva_authority_person |> datatable(
    style = "bootstrap4", # "bootstrap" or "bootstrap4" or "auto" (for bslib)
    class = "table-bordered table-condensed table-sm",
    rownames = FALSE,
    height = "100%",
    escape = FALSE,
    extensions = "RowGroup",
    options = list(
#      rowGroup = list(dataSrc = 0),  # if rownames are used, increase index!
      paging = FALSE,
      dom = "iftr"  # display number of records at top
    ),
    selection = "none"
  )

# Available "dom" settings:
# l - length changing input control
# f - filtering input
# t - The table!
# i - Table information summary
# p - pagination control
# r - processing display element

bs4_card(my_dt5, "Missing authority person identifiers")

```

## Publications missing kthid for author with ORCiD

Some publications from an author with a given ORCiD may sometimes have a kthid associated, but sometimes it is missing on certain publications while being present on others.

:::{.callout-note}
Note that an author with a known ORCiD will likely have a single kthid associated. However, sometimes such information is missing in DiVA on certain publications, but it is present on other publications.
:::

```{r}
#| label: tbl-pubs-missing-kthid
#| tbl-cap: "Authors with kthid but missing DiVA authority person identifier"
#| message: false
#| column: screen-inset-shaded

my_dt3 <- 
  pubs_missing_kthid |> datatable(
    style = "bootstrap4", # "bootstrap" or "bootstrap4" or "auto" (for bslib)
    class = "table-bordered table-condensed table-sm",
    rownames = FALSE,
    height = "100%",
    escape = FALSE,
    extensions = "RowGroup",
    options = list(
#      rowGroup = list(dataSrc = 0),  # if rownames are used, increase index!
      paging = FALSE,
      dom = "iftr"  # display number of records at top
    ),
    selection = "none"
  )

# Available "dom" settings:
# l - length changing input control
# f - filtering input
# t - The table!
# i - Table information summary
# p - pagination control
# r - processing display element

bs4_card(my_dt3, "Publications missing kthids")

```

## Ambiguous ORCiDs

Certain ORCiDs are associated with more than one author at KTH and sometimes also with several "local authority identifiers" in DiVA.

:::{.callout-note}
Note that a KTH author may be associated with zero, one (preferably) or in some cases more than one ORCiDs. However, if more than one KTH author identifier make use of the same ORCiD identifier there are chances that an incorrect affiliation has been detected.
:::

```{r}
#| label: tbl-orcid
#| tbl-cap: "ORCiDs with more than one kthid"
#| message: false
#| column: screen-inset-shaded

my_dt <- 
  kthcorpus:::check_ambiguous_use_orcid() |> datatable(
    style = "bootstrap4", # "bootstrap" or "bootstrap4" or "auto" (for bslib)
    class = "table-bordered table-condensed table-sm",
    rownames = FALSE,
    height = "100%",
    escape = FALSE,
    extensions = "RowGroup",
    options = list(
      rowGroup = list(dataSrc = 0),  # if rownames are used, increase index!
      paging = FALSE,
      dom = "iftr"  # display number of records at top
    ),
    selection = "none"
  )

# Available "dom" settings:
# l - length changing input control
# f - filtering input
# t - The table!
# i - Table information summary
# p - pagination control
# r - processing display element

bs4_card(my_dt, "ORCiD Table")

```

## Stale organisational units

Certain authors have publications that are associated with "closed" or no longer valid organisational units at KTH. These authors also have other publications tagged with an "open" or valid organisational unit, and have more than 10 publications, so may be "low hanging fruit" for retagging.

:::{.callout-note}
Note that authors can have made some publications that were tagged with an organisational unit at KTH that is closed (or was closed, at the time, based on the publication year) and therefore is/were not valid. If such an "invalid" DiVA organisations was closed more than 1.5 years earlier compared to the publication year, there may be more recent organisational units that are better to use. Candidates for suggested valid organisational units that are associated with other publications from the same author are provided below.   
:::




```{r}
#| label: tbl-orgid
#| tbl-cap: "Authors with stale organisational units"
#| message: false
#| column: screen-inset-shaded

my_dt2 <- 
  kthcorpus:::check_invalid_orgid() |> datatable(
    style = "bootstrap4", # "bootstrap" or "bootstrap4" or "auto" (for bslib)
    class = "table-bordered table-condensed table-sm",
    rownames = FALSE,
    height = "100%",
    escape = FALSE,
    options = list(
      paging = FALSE,
      dom = "iftr"  # display number of records at top
    ),
    selection = "none"
  )

# Available "dom" settings:
# l - length changing input control
# f - filtering input
# t - The table!
# i - Table information summary
# p - pagination control
# r - processing display element

bs4_card(my_dt2, "Stale OrgId Table")

```

:::
